Full Brain Blood-Oxygen-Level-Dependent Signal Parameter Estimation Using Particle Filters

### 2010-08-24 doc/paper/main.tex
added correct error range for the simulations

%TODO double check the error measurement, add min/max/mean errors for the runs
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{|c | c | c | c | c | c | c | }
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$ \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  \\
\hline
\hline
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 \\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 \\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 \\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 \\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 \\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 \\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 \\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 \\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 \\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 \\
\hline
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 \\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 separate 310.8 second runs. 
    True value in first row,
    and average in last.}
\label{tab:LowNoiseResults}
\end{table}

%TODO fill in errors
The final square root Mean-Squared-Error (between the estimated and 
noiseless BOLD signal) for the 2400s run was %TODO
and the final correlation matrix is shown in \autoref{tab:long_corr}.

The final parameter estimates of the 310.8s runs are shown in
\autoref{tab:LowNoiseResults}; the square-root MSE for these
parameters ranged from $0.002833$ to $0.003345$, with a mean of 
$0.003066$. Peak signals reached levels of $0.025$.

>>>>

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{|c | c | c | c | c | c | c | }
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$ \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  \\
\hline
\hline
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 \\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 \\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 \\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 \\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 \\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 \\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 \\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 \\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 \\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 \\
\hline
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 \\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 separate 310.8 second runs. 
    True value in first row,
    and average in last.}
\label{tab:LowNoiseResults}
\end{table}

The final square root Mean-Squared-Error (between the estimated and 
noiseless BOLD signal) for the 2400s run was $0.00381$, signal
peaks were $0.035$
and the final correlation matrix is shown in \autoref{tab:long_corr}.

The final parameter estimates of the 310.8s runs are shown in
\autoref{tab:LowNoiseResults}; the square-root MSE for these
parameters ranged from $0.00147$ to $0.0027$, with a mean of 
$0.00217$. Peak signals reached levels of $0.025$.
